Fail Faster

### 2025-03-21 paper/paper.tex
blah

We lay a path forward.
First, we show how to use \textit{multi-stage programming}---a classic technique for 
building fast DSLs “without regret”~\cn{}---to eliminate the overhead of 
many common generator abstractions.
Second, we show that entropy source is an undervalued consideration in generator library design
by isolating the performance contribution of the \rand in generation time, and providing an alternative
that behaves equivalently with $5.5\times$ speedups.
These insights culminate in \name, a recipe for building generator libraries that marry high-level design
with low-level performance.

>>>>

We lay a path forward.
First, we show how to use \textit{multi-stage programming}---a classic technique for 
building fast DSLs “without regret”~\cn{}---to eliminate the overhead of 
many common generator abstractions.
Second, we demostrate that entropy source is an undervalued consideration in generator library design
by isolating its performance contribution, and showing that significant
speedups are possible.
These insights culminate in \name, a recipe for building generator libraries that marry high-level design
with low-level performance.
